|

### 2022-12-29 paper.Rmd
Thu Dec 29 22:00:06 CET 2022: update-remote.sh

```{bash compile_mermaid, include=FALSE}
# Loop through all files with the .mmd extension in the current directory

for file in ./mermaid/*.mmd
do
  # Call PROG on the current file, saving the output as a .png file
  mmdc -i "$file" -o ./img/flowcharts/$(basename "$file" .mmd).png -t light -b transparent 
done

>>>>

```{bash compile_mermaid, include=FALSE}
# compile all *.mmd files in the mermaid directory

WIDTH=1600
HEIGHT=1200
THEME="neutral"
BACKGROUND="transparent"

for file in ./mermaid/*.mmd
do
  mmdc -i "$file" -o ./img/flowcharts/$(basename "$file" .mmd).png -t $THEME -w $WIDTH -H $HEIGHT -b $BACKGROUND 
done
